\section{Additional Details}
\label{sec:appendix}

This appendix is condensed to focus on the main methodological and empirical
contributions. Detailed proofs, extended diagnostics, and expanded
matching/periodicity robustness outputs are provided in supplementary material
(Supplementary Sections S0--S7).

\subsection{Proof/Derivation Locations for Deferred Results in Section \ref{sec:model}}
\label{sec:appendix:proofs}

\subsubsection{Formal derivation for the influence--persistence implication}
\label{app:proof-tradeoff}
Full statement and proof moved to supplementary material (Sections S0.2.1 and
S1.1).

\subsubsection{Proof of the root-special expected thread-size proposition}
\label{app:proof-thread-size}
Full statement and proof moved to supplementary material (Sections S0.2.2 and
S1.2).

\subsubsection{Formal derivation for the periodic detectability implication}
\label{app:proof-periodicity}
Full statement and proof moved to supplementary material (Sections S0.2.3 and
S1.3).

\subsection{Operational Estimation Settings (Methods Details)}
\label{sec:appendix:operational-details}

Operational settings (coverage rules, periodicity preprocessing, bootstrap
configuration, and matching mechanics) are reported in supplementary material.

\subsection{Model Extensions for Future Estimation (Condensed)}
\label{sec:model:extensions}

Richer extensions (hierarchical random effects, re-entry self-excitation, and
visibility-weighted parent assignment) are formalized in supplementary material
(Section S2). The main manuscript uses stratified pooled summaries for
identification clarity in this first-week snapshot.

\subsection{Submolt Categorization (Condensed)}
\label{sec:appendix:submolts}

Submolts are assigned by a fixed deterministic priority rule. The full
keyword-trigger dictionary is moved to supplementary material (Table S1).
\label{tab:submolt-examples}

\subsection{Periodicity Robustness Details}
\label{sec:appendix:periodicity-robustness}

Supplementary PSD diagnostics on the same contiguous segment give AR(1)-
calibrated target-frequency \(p\)-values of 0.508 (5-minute bins), 0.501
(15-minute bins), and 0.556 (30-minute bins). Dominant non-4-hour periods vary
across binning choices (approximately 5.33 to 8.0 hours). The full robustness
plot and settings are provided in supplementary material (Figure S1).

\subsection{Reddit Baseline Supplementary Diagnostics (Condensed)}
\label{sec:appendix:reddit-details}

Under the same estimators, Reddit shows deeper threads (mean maximum depth
2.17), higher direct-reply incidence (36.2\%), and longer kernel half-life
diagnostic values (2.61 hours; 95\% CI: [2.29, 2.95]) than Moltbook. Expanded Reddit
geometry, survival, and periodicity diagnostics are provided in supplementary
material (Section S3).

\subsection{Cross-Platform Matching: Condensed Diagnostics}
\label{sec:appendix:comparison-details}

Deterministic coarse matching produces 813 pairs in overlap support. Because
only 2.34\% of Moltbook threads are represented, this comparison is contextual
and non-causal. Expanded flow and balance diagnostics are moved to
supplementary material (Section S4).
\label{tab:cross-platform-paired-effects}

\subsection{Matched-Subset Kernel Half-Life Diagnostic}
\label{sec:appendix:match-halflife}

Matched-subset kernel half-life diagnostics are reported in supplementary material
(Section S4.3); this appendix keeps only the reference label used by the main
text.
