\section{Limitations and Ethical Considerations}
\label{sec:limitations}

We discuss the principal limitations of this study and the main ethical
considerations in analyzing AI-agent social-network activity.

\subsection{Limitations}
\label{sec:limitations:limitations}

Scope and identification constraints are consolidated in this section.
This analysis is based on a first-week snapshot of Moltbook (January 28--February 4,
2026) rather than a longitudinal panel. The observation window also contains a
41.72-hour coverage gap, which limits periodicity resolution and can leave reply
opportunities unobserved around the gap interval. Estimates of reply incidence,
reply timing, and thread duration should therefore be interpreted as conditional
on observed coverage in this early period.

Cross-platform evidence remains observational. The matched comparison controls only
coarse topic class, UTC posting hour, and early engagement, leaving residual
confounding from exposure, ranking, moderation, and finer semantic differences.
External validity is also narrow because only a small overlap region is matchable,
and Reddit curation introduces known caveats (including records dropped for missing
submission IDs and a small number of collection request errors). Accordingly,
matched cross-platform results are used as secondary contextual evidence rather
than as the study's core causal pillar.

Behavioral attribution and model specification are necessarily simplified. We cannot
fully separate autonomous agent behavior from human-guided operation, and the
baseline exponential-kernel formulation is an intentionally coarse representation
of timing dynamics. \Cref{sec:model:extensions} records richer
hierarchical, re-entry, and visibility-weighted formulations that are appropriate
for future estimation under longer windows and richer exposure data.

\subsection{Ethical Considerations}
\label{sec:limitations:ethics}

The study uses publicly available Moltbook data and archive-based Reddit data
without attempting to identify human operators behind accounts. Analysis is focused
on aggregate interaction patterns, and Reddit usernames are anonymized in curated
outputs.

Findings about persistence dynamics could be misused to engineer artificial
engagement or conceal weak coordination. To mitigate this risk, the manuscript
emphasizes descriptive and mechanistic interpretation over optimization guidance
and reports uncertainty and identification limits explicitly.

The work has dual-use implications. Better understanding of multi-agent persistence
can support beneficial system design (for example, improved memory and coordination
scaffolds) while also informing more capable autonomous interaction systems.
Given that the underlying behaviors are publicly observable, we treat transparent,
well-qualified analysis as the most responsible scientific approach.
