\section{Reproducibility}
\label{sec:reproducibility}

We are committed to open and reproducible research. This section documents resources for reproducing our analysis.

\subsection{Data Availability}
\label{sec:reproducibility:data}

\paragraph{Moltbook Observatory Archive.} Our primary dataset is publicly available on Hugging Face:
\begin{center}
\url{https://huggingface.co/datasets/SimulaMet/moltbook-observatory-archive}
\end{center}
The dataset is released under the MIT license. We provide a download/export script (\texttt{scripts/download\_moltbook\_observatory\_archive.py}) that fetches and exports the required tables to local storage and writes an export manifest (timestamp, dataset identifier, and exported splits).

\paragraph{Reddit comparison data.} Due to Reddit's terms of service, we cannot redistribute raw Reddit data. Instead, we provide run-scoped curated artifacts and manifests. For the Reddit full-scale run in this manuscript
(\texttt{attempt\_scaled\_20260206-142651Z}), we provide:
\begin{itemize}
    \item Curated submissions/comments tables partitioned by \texttt{run\_id},
    \item Validation output
    (\texttt{outputs/reddit\_only/attempt\_scaled\_20260206-142651Z/validation\_results\_20260206T\_orchestrator.json}),
    \item Analysis summary and run manifest
    (\texttt{outputs/reddit\_only/attempt\_scaled\_20260206-142651Z/tables/analysis\_summary.json},
    \texttt{outputs/reddit\_only/attempt\_scaled\_20260206-142651Z/run\_manifest.json}),
    \item Derived features and manuscript-facing figures/tables under
    \texttt{data\_features/reddit\_only/attempt\_scaled\_20260206-142651Z/} and
    \texttt{outputs/reddit\_only/attempt\_scaled\_20260206-142651Z/}.
\end{itemize}

\paragraph{Processed datasets.} We intend to release processed intermediate datasets (thread trees, survival times, computed metrics) in Parquet format to enable reproduction without re-running preprocessing, subject to platform terms of service and licensing constraints.

\subsection{Code Availability}
\label{sec:reproducibility:code}

All code associated with this manuscript is available in our repository:
\begin{center}
\url{https://github.com/AysajanE/moltbook-persistence}
\end{center}

The repository includes:
\begin{itemize}
    \item \texttt{scripts/}: Data download/export and arXiv bundling utilities.
    \item \texttt{analysis/}: Analysis entrypoints (added as the pipeline stabilizes; see \texttt{analysis/README.md} for current status).
    \item \texttt{paper/}: \LaTeX{} source for this manuscript.
    \item \texttt{requirements.txt}: Python dependencies (minimum versions).
\end{itemize}

\subsection{Computational Environment}
\label{sec:reproducibility:environment}

The Moltbook and Reddit results reported in \Cref{sec:results} were generated on:
\begin{itemize}
    \item OS/architecture: macOS 15.6.1 (arm64),
    \item Python: 3.13.5 for canonical runs; code target/lint baseline is Python
    3.11 (\texttt{ruff target-version = py311} in \texttt{pyproject.toml}),
    \item Key packages: \texttt{numpy 2.4.2}, \texttt{pandas 2.3.3},
    \texttt{scipy 1.17.0}, \texttt{lifelines 0.30.1},
    \texttt{matplotlib 3.10.8}, \texttt{seaborn 0.13.2}.
\end{itemize}
Project dependencies and minimum versions remain listed in \texttt{requirements.txt}.

\subsection{Reproducing Key Results}
\label{sec:reproducibility:reproduce}

To reproduce the workflows reported in this manuscript version:

\begin{enumerate}
    \item \textbf{Environment setup:}
    \begin{verbatim}
    python -m venv .venv
    source .venv/bin/activate
    pip install -r requirements.txt
    \end{verbatim}

    \item \textbf{Data download:}
    \begin{verbatim}
    python scripts/download_moltbook_observatory_archive.py \
        --out-dir data/raw/moltbook-observatory-archive
    \end{verbatim}

    \item \textbf{Run Moltbook-only analysis (produces derived tables/figures/manifest):}
    \begin{verbatim}
    python analysis/06_moltbook_only_analysis.py \
        --snapshot-root data_curated/hf_archive/snapshot_20260204-234429Z \
        --data-features-root data_features/moltbook_only \
        --outputs-root outputs/moltbook_only \
        --run-id run_20260206-145240Z \
        --seed 20260206 --bootstrap-reps 400 --ar1-sims 2000
    \end{verbatim}

    \item \textbf{Validate curated Reddit run \texttt{attempt\_scaled\_20260206-142651Z}:}
    \begin{verbatim}
    python analysis/05_reddit_validate.py \
        --curated-root data_curated/reddit \
        --run-id attempt_scaled_20260206-142651Z \
        --request-log data_raw/reddit/2026-02-06/request_log/attempt_scaled_20260206-142651Z.jsonl \
        --out outputs/reddit_only/attempt_scaled_20260206-142651Z/validation_results_20260206T_orchestrator.json
    \end{verbatim}

    \item \textbf{Run Reddit-only analysis entrypoint 07:}
    \begin{verbatim}
    python analysis/07_reddit_only_analysis.py \
        --curated-root data_curated/reddit \
        --run-id attempt_scaled_20260206-142651Z \
        --outputs-root outputs/reddit_only \
        --data-features-root data_features/reddit_only \
        --ops-root outputs/ops \
        --seed 20260206 --bootstrap-reps 400 --ar1-sims 2000
    \end{verbatim}

    \item \textbf{Build the paper PDF (requires a local \LaTeX{} toolchain):}
    \begin{verbatim}
    make paper
    \end{verbatim}

    \item \textbf{Build a timestamped arXiv source bundle:}
    \begin{verbatim}
    make arxiv-bundle
    \end{verbatim}
\end{enumerate}

Canonical runs used for manuscript values in this revision are
\texttt{run\_20260206-145240Z} (Moltbook) and
\texttt{attempt\_scaled\_20260206-142651Z} (Reddit). Moltbook manifest:
\texttt{outputs/moltbook\_only/run\_20260206-145240Z/run\_manifest.json}
and summary:
\texttt{outputs/moltbook\_only/run\_20260206-145240Z/tables/analysis\_summary.json}.
Reddit manifest:
\texttt{outputs/reddit\_only/attempt\_scaled\_20260206-142651Z/run\_manifest.json},
summary:
\texttt{outputs/reddit\_only/attempt\_scaled\_20260206-142651Z/tables/analysis\_summary.json},
and validation:
\texttt{outputs/reddit\_only/attempt\_scaled\_20260206-142651Z/validation\_results\_20260206T\_orchestrator.json}.

\subsection{Versioning and Archival}
\label{sec:reproducibility:versioning}

Upon publication, we will:
\begin{itemize}
    \item Archive the repository on Zenodo with a permanent DOI.
    \item Tag the release corresponding to the published paper version.
    \item Include checksums for downloaded data files to verify integrity.
\end{itemize}

\subsection{Contact}
\label{sec:reproducibility:contact}

For questions about reproducing this work, please contact the corresponding author or open an issue on the GitHub repository.
