\section{Results}
\label{sec:results}

We present our findings organized around the four research themes: conversation geometry, interaction half-life, periodicity detection, and cross-platform comparison.

\subsection{Conversation Geometry on Moltbook}
\label{sec:results:geometry}

\subsubsection{Depth Distribution}

\todo{Insert figure: depth distribution histogram with exponential fit.}

Moltbook conversations are notably shallow. \Cref{fig:depth-distribution} shows the distribution of maximum thread depth $D_j$ across all threads with at least one comment.

\begin{itemize}
    \item Mean depth: \todo{X.XX} (95\% CI: \todo{[X.XX, X.XX]})
    \item Median depth: \todo{X}
    \item Proportion reaching depth 5+: \todo{X\%}
    \item Proportion reaching depth 10+: \todo{X\%}
\end{itemize}

Fitting the exponential tail bound $\Prob(D_j \geq k) \leq \mu^k$ yields an estimated branching ratio of $\hat{\mu} = $ \todo{0.XX}, indicating a strongly subcritical regime.

\subsubsection{Branching Factor by Depth}

\todo{Insert figure: mean branching factor by depth level.}

\Cref{fig:branching-by-depth} shows the mean number of children for nodes at each depth level. The root post receives an average of \todo{X.X} direct replies, but branching factor declines sharply: depth-1 nodes average \todo{X.X} children, and depth-2 nodes average only \todo{X.X}. This pattern is consistent with star-shaped conversation trees where most engagement concentrates at the root.

\subsubsection{Reciprocity and Re-Entry}

Dyadic reciprocity (bidirectional replies between agent pairs) is low: only \todo{X\%} of dyads appearing in the same thread exhibit mutual replies. The median reciprocal chain length is \todo{1}, indicating that extended back-and-forth exchanges are rare.

The thread-level re-entry rate has mean \todo{0.XX} and median \todo{0.XX}. Most threads involve distinct agents for each comment, with minimal return engagement from participants. \Cref{fig:reentry-distribution} shows the distribution of $\text{RE}_j$.

\todo{Insert figure: re-entry rate distribution.}

\subsection{Interaction Half-Life}
\label{sec:results:halflife}

\subsubsection{Overall Estimate}

\todo{Insert figure: survival curve with fitted exponential.}

Fitting the exponential survival model to all inter-reply times yields:
\begin{align*}
\hat{\beta} &= \todo{0.XXX} \text{ hr}^{-1} \quad \text{(95\% CI: \todo{[0.XXX, 0.XXX]})} \\
\hat{h} &= \frac{\ln 2}{\hat{\beta}} = \todo{X.X} \text{ hours} \quad \text{(95\% CI: \todo{[X.X, X.X]})}
\end{align*}

The estimated half-life of approximately \todo{4} hours aligns with the hypothesized heartbeat-driven attention clock. \Cref{fig:survival-curve} shows the empirical survival function alongside the fitted exponential model.

\subsubsection{Weibull Shape Parameter}

The Weibull model yields shape parameter $\hat{\gamma} = $ \todo{X.XX} (95\% CI: \todo{[X.XX, X.XX]}). A value \todo{near 1 / significantly different from 1} \todo{supports / contradicts} the exponential assumption. \todo{Interpret based on actual results.}

\subsubsection{Stratification by Submolt Category}

\todo{Insert table: half-life by submolt category.}

\Cref{tab:halflife-by-submolt} shows estimated half-lives stratified by submolt category.

\begin{table}[t]
\centering
\caption{Interaction half-life by submolt category. \todo{Update with actual estimates.}}
\label{tab:halflife-by-submolt}
\small
\begin{tabular}{@{}lrrrr@{}}
\toprule
\textbf{Category} & \textbf{Threads} & \textbf{Comments} & \textbf{Half-life (hr)} & \textbf{95\% CI} \\
\midrule
Builder/Technical & \todo{--} & \todo{--} & \todo{X.X} & \todo{[X.X, X.X]} \\
Philosophy/Meta & \todo{--} & \todo{--} & \todo{X.X} & \todo{[X.X, X.X]} \\
Social/Casual & \todo{--} & \todo{--} & \todo{X.X} & \todo{[X.X, X.X]} \\
Creative & \todo{--} & \todo{--} & \todo{X.X} & \todo{[X.X, X.X]} \\
Spam/Low-Signal & \todo{--} & \todo{--} & \todo{X.X} & \todo{[X.X, X.X]} \\
\midrule
Overall & \todo{--} & \todo{--} & \todo{X.X} & \todo{[X.X, X.X]} \\
\bottomrule
\end{tabular}
\end{table}

\todo{Describe pattern: do builder/technical submolts show longer half-lives as hypothesized?}

\subsubsection{Agent Heterogeneity}

The mixed-effects model reveals substantial agent-level variation in decay rates. The estimated standard deviation of log-decay rates is $\hat{\sigma}_\beta = $ \todo{X.XX}, corresponding to a \todo{X}-fold range in half-lives across agents at the 5th--95th percentile.

High-karma agents (top quartile) exhibit \todo{longer / similar / shorter} half-lives than low-karma agents: \todo{X.X} hours vs.\ \todo{X.X} hours ($p$ \todo{< / =} \todo{0.XX}).

\subsection{Periodicity Detection}
\label{sec:results:periodicity}

\subsubsection{Spectral Analysis}

\todo{Insert figure: power spectral density with annotated peaks.}

\Cref{fig:psd} shows the power spectral density of aggregate comment activity. We observe \todo{a significant peak / no significant peak} at frequency $f \approx 0.25$ hr$^{-1}$ (period $\approx 4$ hours). The peak-to-background ratio is \todo{X.X} (Fisher's $g = $ \todo{X.XX}, $p$ \todo{< / =} \todo{0.XX}).

\todo{If peak detected: This provides direct evidence that the heartbeat mechanism induces periodic structure in platform activity.}

\todo{If no peak: The expected periodic signature is not detected, possibly due to jitter in agent check-in times, asynchronous heartbeat phases, or dominance of other temporal patterns.}

\subsubsection{Agent-Level Autocorrelation}

Among agents with $\geq 10$ comments, the mean autocorrelation of inter-comment times at lag 4 hours is \todo{X.XX} (95\% CI: \todo{[X.XX, X.XX]}). \todo{Describe pattern: is there elevated autocorrelation at heartbeat lags?}

\subsection{Cross-Platform Comparison}
\label{sec:results:comparison}

\subsubsection{Matched Sample Characteristics}

After coarsened exact matching, our comparison sample comprises \todo{N} Moltbook--Reddit pairs. Balance diagnostics confirm successful matching: standardized mean differences for matching variables are all below 0.1. \todo{Insert balance table in appendix if needed.}

\subsubsection{Half-Life Comparison}

\todo{Insert figure: paired comparison of half-lives.}

\Cref{fig:halflife-comparison} compares estimated half-lives between matched Moltbook and Reddit threads.

\begin{itemize}
    \item Moltbook median half-life: \todo{X.X} hours
    \item Reddit median half-life: \todo{X.X} hours
    \item Paired difference: \todo{X.X} hours shorter on Moltbook (Wilcoxon $p$ \todo{<} \todo{0.XX})
    \item Effect size: Cliff's $\delta = $ \todo{X.XX} (\todo{small / medium / large})
\end{itemize}

\subsubsection{Structural Comparison}

\Cref{tab:platform-comparison} summarizes structural differences between platforms.

\begin{table}[t]
\centering
\caption{Structural comparison between matched Moltbook and Reddit threads. \todo{Update with actual values.}}
\label{tab:platform-comparison}
\small
\begin{tabular}{@{}lrrrl@{}}
\toprule
\textbf{Metric} & \textbf{Moltbook} & \textbf{Reddit} & \textbf{Difference} & \textbf{$p$-value} \\
\midrule
Mean depth & \todo{X.X} & \todo{X.X} & \todo{X.X} & \todo{<0.XX} \\
Mean comments & \todo{X.X} & \todo{X.X} & \todo{X.X} & \todo{<0.XX} \\
Re-entry rate & \todo{0.XX} & \todo{0.XX} & \todo{0.XX} & \todo{<0.XX} \\
Reciprocity & \todo{X\%} & \todo{X\%} & \todo{X\%} & \todo{<0.XX} \\
Half-life (hr) & \todo{X.X} & \todo{X.X} & \todo{X.X} & \todo{<0.XX} \\
\bottomrule
\end{tabular}
\end{table}

Moltbook threads are \todo{shallower, shorter, and less reciprocal} than their Reddit counterparts across all metrics, with \todo{large} effect sizes.

\subsubsection{Sensitivity Analyses}

Results are robust to:
\begin{itemize}
    \item Stricter matching (exact match on early comment count): half-life difference \todo{persists / attenuates} (\todo{X.X} vs.\ \todo{X.X} hours).
    \item Excluding suspected spam periods on Moltbook: half-life estimate \todo{increases slightly to X.X hours / remains stable}.
    \item Alternative estimation (Cox regression): hazard ratio for Moltbook vs.\ Reddit is \todo{X.X} (95\% CI: \todo{[X.X, X.X]}).
\end{itemize}

\subsection{Summary of Key Findings}
\label{sec:results:summary}

Our analysis yields the following principal findings:

\begin{enumerate}
    \item \textbf{Short half-life}: Moltbook exhibits an interaction half-life of approximately \todo{4} hours, substantially shorter than matched Reddit threads (\todo{X} hours).

    \item \textbf{Shallow structure}: Conversation trees are star-shaped with median depth \todo{2--3} and rapidly declining branching factors.

    \item \textbf{Limited reciprocity}: Dyadic reciprocity and re-entry rates are low, indicating single-shot rather than conversational engagement.

    \item \textbf{Periodic signatures}: \todo{Evidence of / No clear evidence of} heartbeat-driven periodicity in aggregate activity.

    \item \textbf{Topic moderation}: \todo{Builder/technical submolts show longer / Categories show similar} half-lives.

    \item \textbf{Agent heterogeneity}: Substantial variation in decay rates across agents, with \todo{weak / moderate} association with reputation.
\end{enumerate}
