\section{Conclusion}
\label{sec:conclusion}
This paper measured how quickly agent conversations fade on Moltbook during its first week of public operation. We operationalized conversational persistence as \emph{direct-reply responsiveness over time}: how rapidly a comment stops attracting direct replies as it ages, separating reply \emph{timing} from the separate question of whether a reply happens at all. In this snapshot, Moltbook discussions are shallow and strongly root-heavy. Most comments receive no direct reply, reciprocal back-and-forth is uncommon, and when replies do arrive they concentrate in the first seconds to minutes. The resulting picture is not slow conversational decay but a ``fast response or silence'' regime, which leaves limited room for extended multi-turn deliberation without additional support.

A widely discussed architectural hypothesis is that Moltbook agents check in on an approximately four-hour heartbeat schedule. Because per-account heartbeat events are not directly observed in the archive, we tested only for \emph{aggregate} periodic signatures. Across contiguous windows and binning choices, we do not detect a statistically reliable four-hour peak in this snapshot. This should be interpreted as a detectability result rather than evidence that periodic schedules do not exist: dephasing, jitter, mixed cadences, and limited contiguous coverage can erase a clean platform-level signature even when individual agents follow periodic routines.

For context, a contemporaneous Reddit corpus analyzed with the same estimators shows substantially deeper threads, higher direct-reply incidence, and reply persistence on the order of hours rather than minutes. A coarse overlap-restricted matching exercise points in the same direction but remains observational and is not a causal attribution of platform differences. The main next step is longitudinal measurement under richer exposure controls (visibility, ranking, notifications) and richer agent-level models, enabling sharper tests of design interventions such as memory aids, thread summarization, and explicit re-entry prompts. Absent such scaffolding, early agent social platforms may remain better at launching interactions than sustaining the conversations required to finish them.
